Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-08-11 paper/paper.tex
20200811 9:24

\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}

\author{\textcolor{cyan}{XXX}}
\affiliation{\textcolor{cyan}{XXX}}

@@

\section{\label{sec:Introduction}Introduction}
Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a "quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripy, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.

In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripy types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

@@

On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}. At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,arXiv1911.08036,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

{
    \color{red}The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK model. The exact diagonalization and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}. Section~\ref{sec:Results} disscuss the main results of this paper.
}

@@

To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform exact-diagonalization calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition. To detect quantum phase transitions, the second derivatives of the GS energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and its singularities are used to identify possible phase transtions.

@@

To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin-coherent states with varying moment directions. The cluster spin-coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
\begin{align}
    |\Psi \rangle = \bigotimes_{i=1}^N | \theta_i, \phi_i \rangle,
    \label{eq:ClusterCoherentState}
\end{align}
where the spin-1/2 coherent state
\begin{align}
    |\theta, \phi\rangle = \mathcal{R}_z(\phi) \mathcal{R}_y(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
    \label{eq:Spin-1/2CoherentState}
\end{align}
is fully polaried state along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles. By calculating the overlap between the exact cluster GS and cluster spin-conherent states, $P = | \langle \Psi | GS \rangle|^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.

@@

In order to better understand the quantum phases identified by the exact diagonalization method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24\times 24$ triangle lattice with periodic boundary conditions. A whole MC step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ MC steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \bm{S}_i = \frac{\bm{h}_i^{loc}}{|\bm{h}_i^{loc}|} S,
\end{align}
with
\begin{align}
    \bm{h}_i^{loc} = \sum_{\langle j \rangle} J \bm{S}_j + K {S}^{\gamma}_j \hat{e}^{\gamma} + \Gamma (S^\alpha_j \hat{e}^{\beta} + S^\beta_j \hat{e}^\alpha),
\end{align}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

From the magnetic configuration of GS, we compute the spin structure factor given by
\begin{align}
    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
\end{align}
which is a key characterizes to identify magnetic phases.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \includegraphics[width=\linewidth]{fig/SecondDerivatives.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details. (b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$. (c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$. (d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
\end{figure*}

The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}(a). The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.

In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases. For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$. As mentioned in Sec.~\ref{sec:Model}, the form of the HK model ($\Gamma=0$) is invariant under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, two more magnetic ordered phases can be identified. When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state. Thus, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$. However, for the phase near the AFM Kitaev point ($J=\Gamma=0$, $K>0$), it is mapped to itself under FST, so we can not identify its magnetic properties with the FST.

When the $\Gamma$ term is included, we find that the stripe phase, the FM phase and the phase near the AFM Kitaev point in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model. Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are six other new phases.

To reveal the natures of these new phases, we perform the classical MC calculations as described in Sec.~\ref{subsec:MethodMC}. For convenience of comparison between the quantum and classical results, we also present the classical phase diagram obtained from the MC simulations in Fig.~\ref{fig:ClassicalPhaseDiagram}, which is consistent with the phase diagram reported in Ref.~\onlinecite{PhysRevB.92.165108}. According to the classical MC results, we can identify that the three new phases with large areas mainly located in the $J>0$ region have stripe orders (i.e., the stripe-B and stripe-C phases), while the two new phases mainly located in the $J<0$ region are FM (i.e., the FM-A and FM-C phases). In addition, we find that the area of the 120$^\circ$ N\'{e}el state in the quantum phase diagram is greatly reduced, and more importantly the extra phase near $\Gamma=1$ that does not exist in the classical phase diagram.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/ClassicalGlobalPhaseDiagram.pdf}
    \caption{\label{fig:ClassicalPhaseDiagram}(Color online) Classical global phase diagram of the $J$-$K$-$\Gamma$ model obtained from classical Monte Carlo simulation.}
\end{figure}

>>>>

\author{Zhongyuan Qi}
\affiliation{College of Physics Science and Technology, Yangzhou University, Yangzhou 225002, China}

\author{Bin Xi}
\affiliation{College of Physics Science and Technology, Yangzhou University, Yangzhou 225002, China}

@@

\section{\label{sec:Introduction}Introduction}

Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbit coupling (SOC), electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}.

In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

@@

On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}. At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

In this paper, we study the global phase diagram and the phase transitions of the triangular-lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit. The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}. Section~\ref{sec:Results} gives the main results of this paper.

@@

To obtain the quantum phase diagram of the model~\eqref{eq:Hamiltonian}, we perform ED calculations of the GS of the Hamiltonian~\eqref{eq:Hamiltonian} on a $4 \times 6$ cluster with the periodic boundary condition. To detect quantum phase transitions, the second derivatives of the GS energy, $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ were computed and its singularities are used to identify possible phase transtions.

@@

To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin coherent states with varying moment directions. The cluster spin coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
\begin{align}
    | \Psi \rangle = \bigotimes_{i=1}^{N} | \theta_{i}, \phi_{i} \rangle,
    \label{eq:ClusterCoherentState}
\end{align}
where the spin-1/2 coherent state
\begin{align}
    | \theta, \phi \rangle = \mathcal{R}_{z}(\phi) \mathcal{R}_{y}(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
    \label{eq:Spin-1/2CoherentState}
\end{align}
is fully polaried state along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles. By calculating the overlap between the exact cluster GS and cluster spin conherent states, $P = | \langle \Psi | GS \rangle |^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.

@@

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \bm{S}_{i} = \frac{\bm{h}_{i}^{loc}}{|\bm{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \bm{h}_{i}^{loc} = \sum_{\langle j \rangle} J \bm{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

From the magnetic configuration of GS, we compute the SSF given by
\begin{align}
    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
\end{align}
which is a key characterizes to identify magnetic phases.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, Modulated Stripe, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
\end{figure*}

The quantum phase diagrams obtained by the ED method for $\Gamma \geq 0$ and $\Gamma \leq 0$ on a $4 \times 6$ cluster with the periodic boundary condition are presented in Fig.~\ref{fig:QuantumPhaseDiagram}. The phase boundaries are determined by the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ (see Appendix \ref{apx:PhaseBoundary} for details).

In the HK limit ($\Gamma=0$), as with the previous study~\cite{KaiLi2015}, we find five quantum phases. For pure Heisenberg models ($K=\Gamma=0$), the GSs are well known, i.e., a FM state for $J<0$ and a 120$^\circ$ N\'{e}el state for $J>0$, respectively. As mentioned in Sec.~\ref{sec:Model}, the HK model ($\Gamma=0$) preserves its form under the FST~\cite{PhysRevB.89.014414} but with different exchange interactions. Thus, by virtue of the FST, two more magnetic ordered phases can be identified. When $\beta=\pi - \arctan\frac{1}{2}$ in Eq.~\eqref{eq:FST}, the FST maps the Hamiltonian~\eqref{eq:Hamiltonian} to FM Heisenberg model of the rotated spin operators $\bm{S}^{\prime}$, whose GS is a FM state. Therefore, transformating back to the original spin basis, a collinear stripe order can be obtained. Similarly, a noncollinear spiral order (Dual N\'{e}el) is obtained from the 120$^\circ$ N\'{e}el order for $\beta=-\arctan\frac{1}{2}$. However, for the phase containing the AFM Kitaev point ($J=\Gamma=0$, $K=1$), since it is mapped to itself under FST, we can not identify its magnetic properties with the FST.

The properties of each quantum phases, especially the spin configuration of the ordered phases, can be inferred from the SSF defined in Eq.~\eqref{eq:SSF}, so we calculate the SSF for the case of pure AFM Kitaev limit ($J=\Gamma=0$, $K=1$) and present the result in Fig.~\ref{fig:StructureFactors}(a). We find that the SSF shows obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). For the sake of clarity, we further perform a ``basin-hopping" global optimization~\cite{jp970984n} on a $12 \times 12$ lattice by taking the spins as classical magnetic moments to search for the possible spin configurations under this set of interaction parameters. The stripe orders are indeed possible GS spin configurations, but there are also many nematic states with the same energy as it at the classical level since the AFM chains are decoupled (see Appendix~\ref{apx:DegeneratedStates} for details). When we consider the quantum fluctuations generated by the Kitaev interactions not along the AFM chains, the $4^{th}$ order corrections will give an effective coupling between the next-nearest-neighbor spins~\cite{PhysRevB.92.184416}, which can stabilize the stripe order. Thus, the degeneracy of the spin configurations is lifted by the order-by-disorder mechanism, and we can identify that the phase containing the AFM Kitaev point of the HK model is a stripe phase, which we label the stripe-C in Fig.~\ref{fig:QuantumPhaseDiagram}. Moreover, every stripe order in this phase can be transformed to another degenerate stripe pattern in the same phase by a FST, so these stripe orders are consistent with the FST.

When the $\Gamma$ term is included, we find that the FM phase and the stripe-C phase in the HK model are actually phase boundaries in the global phase diagram of the $J$-$K$-$\Gamma$ model. Moreover, except the 120$^\circ$ N\'{e}el state and the dual N\'{e}el state, which already exist in the HK limit, there are five other new phases according to the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.
